An upper bound to gas storage and delivery via pressure-swing adsorption in porous materials

### 2021-09-04 gas-adsorption/rsc-gas-ads-complete.tex
last edits?
structure prop rel.

\startreferees{Added discussion of screening studies}
Finally, in a number of studies, molecular simulations of gas adsorption in
a large pool of both existing and predicted nanoporous
structures empirically shed light on performance limitations \cite{firlej2013understanding, goldsmith2013theoretical,
ahmed2019exceptional,simon2015materials}.
Such studies can guide the development of new materials
by allowing researchers to identify commonalities among materials that have
desirable properties.  
However, the largest observed simulated deliverable capacity among the pool of candidate materials in such studies
is only a \emph{lower bound} on the highest attainable deliverable capacity that is is predicted upon the accuracy of the molecular models.
\donereferees

@@

Fig.~\ref{fig:methane-298-D} clearly shows that $\V_{opt}$ provides a maximum
$\rho_D$ over all \emph{spatially uniform}, static potential energy fields. To
qualitatively argue that the spatially uniform potential $\V_{opt}$ provides a
maximum deliverable capacity over \emph{all} (including non-spatially uniform)
static potential energy fields (a broader claim), consider a
non-spatially-uniform variation on $\V_{opt}$. 
At low adsorbed gas densities, the lowest-energy positions will be preferentially occupied, while
at higher densities, the additional gas molecules will be forced into higher
energy locations. Thus, the mean attraction will be lowest at \pfull\ and
highest at \pempty. 
Therefore, the effect of a non-spatially uniform variation on $\V_{opt}$ is to reduce the deliverable capacity.
By the same argument, $\gst$ increases monotonically with
pressure. As shown in Sec.~\ref{sec:monotonic}, this results in
the deliverable capacity provided by a non-uniform potential with a given $\gst$ at $\pfull$ or $\pempty$ being lower than the
deliverable capacity provided by a uniform potential with $\V=\gst$. Thus, a spatially uniform potential gives the maximal
deliverable capacity amongst all static potential energy fields that give the
same $\gst$, and the \emph{optimal} uniform potential $\V_{opt}$ will yield a
greater deliverable capacity over any static, non-uniform potential.

@@

\startreferees{Added an explanation of why we cannot place a bound on the
  deliverable capacity when the temperature is changed.}

@@

>>>>

Finally, in a number of studies, molecular simulations of gas adsorption in
a large pool of both existing and predicted nanoporous
structures empirically shed light on performance limitations \cite{firlej2013understanding, goldsmith2013theoretical,
ahmed2019exceptional,simon2015materials}.
Such studies can guide the development of new materials
by allowing researchers to identify commonalities among materials that have
desirable properties.  
However, the largest observed simulated deliverable capacity among the pool of candidate materials in such studies
is only a \emph{lower bound} on the highest attainable deliverable capacity that is is predicted upon the accuracy of the molecular models.

@@

Fig.~\ref{fig:methane-298-D} shows that $\V_{opt}$ provides a maximum
$\rho_D$ over all \emph{spatially uniform}, static potential energy fields. To
qualitatively argue that the spatially uniform potential $\V_{opt}$ provides a
maximum deliverable capacity over \emph{all} (including non-spatially uniform)
static potential energy fields (a broader claim), consider a
non-spatially-uniform variation on $\V_{opt}$. 
At low adsorbed gas densities, the lowest-energy positions will be preferentially occupied, while
at higher densities, the additional gas molecules will be forced into higher
energy locations. Thus, the mean attraction will be lowest at \pfull\ and
highest at \pempty. 
Therefore, the effect of a non-spatially uniform variation on $\V_{opt}$ is to reduce the deliverable capacity.
By the same argument, $\gst$ increases monotonically with
pressure. As shown in Sec.~\ref{sec:monotonic}, this results in
the deliverable capacity provided by a non-uniform potential with a given $\gst$ at $\pfull$ or $\pempty$ being lower than the
deliverable capacity provided by a uniform potential with $\V=\gst$. Thus, a spatially uniform potential gives the maximal
deliverable capacity amongst all static potential energy fields that give the
same $\gst$, and the \emph{optimal} uniform potential $\V_{opt}$ will yield a
greater deliverable capacity over any static, non-uniform potential.

@@

@@

\startreferees{Explain how the point of our paper is not to find structure-property relationships.}

Several studies elucidated relationships between structural features of nanoporous materials---such as void fraction, pore size, and surface area---and their deliverable capacity of various gases \cite{gomez2014exploring,ahmed2019exceptional,simon2015materials,moghadam2018computer,Tong2018}. 
Such structure-property relationships serve as useful heuristics for designing new materials with high deliverable capacity. However, the intention of our paper is not to discover structure-property relationships. 
Rather, we place our upper bound on the deliverable capacity of [rigid] materials that holds irrespective of how the structural features of the material are tuned.
